Is high social class always beneficial for survival? Northern Sweden 1801--2013

### 2018-02-28 article3c.Rmd
marginal efforts

A alternative, and preferable, approach is the marginal model, where the disturbace effect of confounders is 
balanced out through weighting. In our case , `civil status` and `urban/rural` are confounders, that is, they 
are correlated to both our outcome, mortality, and our explanatory variable, social class. The latter association 
manifests itself through the facts that the marriage frequency varies social class and certain social classes are 
more common in the rural area than others (we find farmers on the countryside).

@@

```{r exweight}
exm <- vb0Tab[vb0Tab$period == "1901-1925" & vb0Tab$sex == "male", c("age", "civst", "urban", "exposure", "event", "hisclass")]
all <- aggregate(exm["exposure"], by = exm[c("civst", "urban", "age")], FUN = sum)
all
```

@@

```{r forelite}
elite <- exm[exm$hisclass == "elite", c("age", "civst", "urban", "exposure", "event", "hisclass")]
el <- aggregate(elite["exposure"], by = elite[, c("civst", "urban", "age")], FUN = sum)
el
```

>>>>

A alternative, and preferable, approach is the marginal model, where the disturbace effect of confounders is 
balanced out through weighting. In our case , `civil status` and `urban/rural` are confounders, that is, they 
are correlated to both our outcome, mortality, and our explanatory variable, social class. The latter association 
manifests itself through the facts that the marriage frequency varies by social class and certain social classes are 
more common in the rural area than others (we find farmers on the countryside).

@@

```{r exweight}
exm <- vb0Tab[vb0Tab$period == "1901-1925" & vb0Tab$sex == "male", c("age", "civst", "urban", "exposure", "event", "hisclass")]
all <- aggregate(exm[, c("exposure", "event")], by = exm[, c("civst", "urban")], FUN = sum)
all
```

@@

```{r forelite}
elite <- exm[exm$hisclass == "elite", c("age", "civst", "urban", "exposure", "event", "hisclass")]
el <- aggregate(elite[, c("exposure", "event")], by = elite[, c("civst", "urban")], FUN = sum)
el
```
